---
title: "Submission2-HW5"
subtitle: "Research Methods, Spring 2024"
author: "Caroline Hansen"
format:
  pdf:
    output-file: "carolinehw5-2"
    output-ext:  "pdf"
    header-includes:
      - \usepackage{float}
      - \floatplacement{table}{H}
---



```{r}
#| include: false
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, readr, readxl, hrbrthemes, fixest,
               scales, gganimate, gapminder, gifski, png, tufte, plotly, OECD,
               ggrepel, survey, foreign, devtools, pdftools, kableExtra, modelsummary,
               kableExtra, webshot2,fixest)
```

```{r}
#| include: false
#| eval: true

load("Hwk5.1_workspace.Rdata")
```


# Answers for Homework 5: Submission 2
\newpage

# Problem 1 
\noindent 1. Plot the share of the adult population with direct purchase health insurance over time.
```{r} 
#| echo: false
#| label: 1problem
#| fig-cap: "Direct Purchase Health Insurance"

problem1

```

# Problem 2
\noindent 2. Discuss the reduction in direct purchase health insurance in later years. Can you list a couple of policies that might have affected the success of the direct purchase insurance market?


The Affordable Care Act lead to people who do not have employer insurance, who might have bought individual insurance otherwise. 


# Problem 3
\noindent 3. Plot the share of the adult population with Medicaid over time.

```{r} 
#| echo: false
#| label: 3problem
#| fig-cap: "Medicaid Over Time"

problem3

```


# Problem 4
\noindent 4. Plot the share of uninsured over time, separately by states that expanded Medicaid in 2014 versus those that did not. Drop all states that expanded after 2014.

```{r} 
#| echo: false
#| label: 4problem
#| fig-cap: "Medicaid Over Time"

problem4

```

# Problem 5
\noindent 5. Calculate the average percent of uninsured individuals in 2012 and 2015, separately for expansion and non-expansion states. Present your results in a basic 2x2 DD table.
```{r} 
#| echo: false
#| label: 5problem
#| fig-cap: "Average Percent of Uninsured Individuals in 2012 and 2015"

options(knitr.kable.NA = 0)
knitr::kable(avg_did, 
             col.names=c("Expansion Status","Percent Uninsured"),
             format.args=list(big.mark=","), booktabs = TRUE) 

```

# Problem 6
\noindent 6. Estimate the effect of Medicaid expansion on the uninsurance rate using a standard DD regression estimator, again focusing only on states that expanded in 2014 versus those that never expanded.
```{r} 
#| echo: false
#| label: 6problem
#| fig-cap: "Medicaid Expansion DD Regression Estimator"
modelsummary(dd.ins.reg,
             coef_rename=c("postTRUE" = "Post 2014","expand_everTRUE"="Expand",
                           "treat" = "Post x Expand"),
             gof_omit='DF|F|Lik|AIC|BIC|Adj')
```

# Problem 7
\noindent 7.I nclude state and year fixed effects in your estimates. Try using the lfe or fixest package to estimate this instead of directly including the fixed effects.

```{r} 
#| echo: false
#| label: 7problem
#| fig-cap: "Medicaid Expansion DD Regression Estimator"

models <- list("Standard DD" = m.dd7, 
               "TWFE" = m.twfe7)
modelsummary(models,
             coef_rename=c("postTRUE" = "Post 2014","expand_everTRUE"="Expand",
                           "treat" = "Post x Expand"))
```


# Problem 8
\noindent 8.Include state and year fixed effects in your estimates. Try using the lfe or fixest package to estimate this instead of directly including the fixed effects.

```{r} 
#| echo: false
#| label: 8problem
#| fig-cap: "Fixed Effects in Estimate"

 msummary(list("DD"=m.dd8, "TWFE"=m.twfe8),
         shape=term + statistic ~ model, 
         gof_map=NA,
         coef_omit='Intercept',
         vcov=~State
         )
```

# Problem 9
\noindent 9.Include state and year fixed effects in your estimates. Try using the lfe or fixest package to estimate this instead of directly including the fixed effects.

```{r} 
#| echo: false
#| label: 9problem
#| fig-cap: "Fixed Effects in Estimate"

iplot(mod.twfe9, 
      xlab = 'Time to treatment',
      main = 'Event study')

```

# Problem 10
\noindent 10.Include state and year fixed effects in your estimates. Try using the lfe or fixest package to estimate this instead of directly including the fixed effects.

```{r} 
#| echo: false
#| label: 10problem
#| fig-cap: "Fixed Effects in Estimate"

iplot(mod.twfe10, 
      xlab = 'Time to treatment',
      main = 'Event study')

```
